An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-14 paper/paper.tex
Paper: Add to the BTBackup section (Churn and Data Migration, Fairness, and Challenge Mechanism). Also add description of salts to the Cryptography section in the Background.

\subsection{Fairness}
Another aspect of P2P backup systems is fairness between peers. Peers need to be storing an amount of data proportional to the amount that they are backing up to other peers. This can be challenging to enforce, because untrustworthy peers can attempt to game the system to obtain free backup storage. For example, consider a simple system where each peer must offer store the same amount of data that they back up on other peers. A peer could claim that all of the storage space that it should be offering is being used by other peers, while in reality the peer has not taken in any other peer's data. It is clear that a mechanism needs to be built into the system that ensures that peers store the data of each other.

@@

\textit{Hashing} is the process of applying a \textit{hash function} to some arbitrary-length message, resulting in a fixed sized \textit{hash}. A good hash function will uniformly distribute the hashes it produces. \textit{Cryptographic hash functions} are hash functions that are suitable for use in cryptography. They possess mathematical properties that allow for confidentiality to be provided, among other properties.

@@

@@

\subsection{Churn and Data Migration} \label{sec:churnanddatamigration}

@@

To solve this problem, peers need to periodically check on the nodes that they are using as backup locations in order to gauge how available they are. During normal program operation, each peer pings its backup locations to see whether or not they are online. If a backup node is found to be online, then the peer does not need to do anything; it will continue to think that it is reliable. If the node is offline, however, the peer will take note that it was unavailable during a ping test, and that the node might be unreliable in general. It would be unfair to immediately conclude that the node is unreliable, since it may have been temporarily offline (for example, a user temporarily shutting down his/her computer). Therefore, a node needs to fail the ping test several times before the peer that uses it concludes that it is unreliable. It is possible that a node gets unlucky and happens to be offline during all checks, even though that it is online during a different part of the day. However, if this is the case, then the node is not frequently available for that node, and should be seen as unreliable.

% TODO: I'm not sure if we need to explain the blacklist here, or if it has already been explained.
When a peer determines that a node is unreliable, it does two things. The first is that it adds its own ID to the node's blacklist in the DHT. The blacklist is a list of peer ID and timestamp pairs, where the peer IDs are the IDs of those who have determined that the node is unreliable and the timestamp is the time when the ID was inserted. This information is used by peers who are considering using the node as a backup location in the future. If the node has too many blacklisters, peers will decide against using that node, and move on to select another node. % Pick up here

\section{Fairness} \label{sec:challenge}

% Introduce terminology: "store" and "back up" (and, further, "node" and "peer")
% People store proportional amount of data compared to how much they are backing up

\subsection{Challenge Mechanism}
% This was copied from the explanation of challenge mechanisms in the background info. We will use it down here instead
%A challenge in PeerStore consists of a randomly-generated number followed by a specified range of bytes in the file being backed up. The node holding the peer's data must take the bytes in the specified range, concatenate the random number with that data, take the hash of it, and return the result to the peer. If the correct answer is returned, then the node has passed the challenge. If the node does not respond or gives the wrong answer, the challenge has been failed. By choosing a random subset of bytes and creating a random number to include in the hash, the node cannot calculate the hash ahead of time and only store that; the whole file must be stored in order to be able to successfully complete all possible challenges.

>>>>

\subsection{Fairness} \label{sec:BackgroundFairness}
Another aspect of P2P backup systems is fairness between peers. Peers need to be storing an amount of data proportional to the amount that they are backing up to other peers. This can be challenging to enforce, because untrustworthy peers can attempt to game the system to obtain free backup storage. For example, consider a simple system where each peer must offer store the same amount of data that they back up on other peers. A peer could claim that all of the storage space that it should be offering is being used by other peers, while in reality the peer has not taken in any other peer's data. It is clear that a mechanism needs to be built into the system that ensures that peers store the data of each other.

@@

\textit{Hashing} is the process of applying a \textit{hash function} to some arbitrary-length message, resulting in a fixed sized \textit{hash}. A good hash function will uniformly distribute the hashes it produces. \textit{Cryptographic hash functions} are hash functions that are suitable for use in cryptography. They possess mathematical properties that allow for confidentiality to be provided, among other properties. To strengthen hashing algorithms, a \textit{salt} can be utilized. A salt is essentially a string of bytes that is randomly picked to be appended to the end of a sequence of data to be hashed. This allows the hashed version of a sequence of data to be different, while still being able to calculate the same hash by applying the same salt. This technique is useful in preventing dictionary attacks, where an attacker has a precomputed list of hashes, and the hash of some data is compared to it in an attempt to find out what the original data is. With a salt, the precomputed hash for the data wll not match, and the list cannot be easily recomputed with the salt, since it is an expensive and lengthy operation.

@@

\subsection{The Metadata Layer} \label{sec:TheMetadataLayer_DataExchange}

@@

\subsection{Churn and Data Migration} \label{sec:ChurnandDataMigration_DataExchange}

@@

% TODO: please pay extra attention during the review of this paragraph; I had to work in references to the challenge system after writing it, so some things might sound awkward.
To solve this problem, peers in our system periodically check on the nodes that they are using as backup locations in order to gauge how available they are. During normal program operation, each peer tests the availability of its backup locations (along with a challenge mechanism, which is described in section \ref{subsec:ChallengeMechanism_Fairness}) to see whether or not they are online. If a backup node is found to be online and it passes the challenge, then the peer does not need to do anything; it will continue to think that it is reliable. If the node is offline or fails the challenge, however, the peer will take note that it was unavailable during an availability test, and that the node might be unreliable in general. It would be unfair to immediately conclude that the node is unreliable, since it may have been temporarily offline (for example, a user temporarily shutting down his/her computer). Therefore, a node needs to fail the ping test several times before the peer that uses it concludes that it is unreliable. It is possible that a node gets unlucky and happens to be offline during all checks, even though that it is online during a different part of the day. However, if this is the case, then the node is not frequently available for that node, and should be seen as unreliable.

% TODO: move this up to the metadata layer section, and combine the first two sentences of this paragraph with the next paragraph.
When a peer determines that a node is unreliable, it does two things. The first is that it adds its own ID to the node's blacklist in the DHT. The blacklist is a list of peer ID and timestamp pairs, where the peer IDs are the IDs of those who have determined that the node is unreliable and the timestamp is the time when the ID was inserted. This information is used by peers who are considering using the node as a backup location in the future. If the node has too many blacklisters (greater than some number \textit{n}), peers will decide against using that node, and move on to select another node. In order to prevent sybil attacks, where a malicious user has many identities and blacklists a node many times, the number of blacklisters should be a nontrivial amount and proportional to the size of the network. In order to prevent nodes from permanently being shut out from the network, entries in the blacklist are removed a set amount of tme after they are inserted; this is accomplished via the timestamp mentioned above.

The second action that the peer takes is to move its replica to a new node. The peer sends an update to the DHT that it is removing the replica on the unreliable node. This accomplishes two things: all other peers in the network can see that the node is storing less data, and the node can see that it no longer needs to store the replica, so it can remove it the next time it checks the DHT for any changes. The peer will then look for a new node to put a replica on, using the same process that was used for creating the original backups (see section \ref{sec:TheMetadataLayer}). Since this process uses a randomly generated salt to help pick the ID of the new node, each node has an equal chance of being selected, assuming that it has enough space to store the replica and is not blacklisted by too many peers. This helps to prevent some nodes from being left out of the selection process.

\section{Fairness} \label{sec:Fairness}
% People store proportional amount of data compared to how much they are backing up
To ensure that each node is being fair (see section \ref{sec:BackgroundFairness}), each node must contribute storage space proportional to the amount that they are backing up. Since a peer will have multiple replicas of each file, the amount of space that a peer offers must be much larger than the amount of unique data that it is backing up. If $n$ backups are maintained for each file and $F$ represents the set of files that a peer backs up, the total amount of space $t$ that the peer must offer can be expressed as:
\begin{equation}
t=n\sum\limits_{i=1}^{|F|} size(F_i)
\end{equation}
There still exists one problem with this mechanism: when the network first starts up, no peer has created any backups, so no one is obligated to store data for other peers. To solve this, our system requires that each peer is obligated to take at least $s$ bytes of data from other peers, regardless of how much data it has backed up. To include this, $t$ can be reexpressed as:
\begin{equation}
t=max(s,n\sum\limits_{i=1}^{|F|} size(F_i))
\end{equation}
When a peer finds a node that has a value of $t$ greater than the size of the file it is trying to replicate, it can choose that node as a replication site, knowing that it will be able to accept the data.

\subsection{Challenge Mechanism} \label{subsec:ChallengeMechanism_Fairness}
Even though the technique described above allows peers to find nodes with a sufficient amount of storage space, it does not guarantee that the node will keep its promise and actually store the data. For instance, a node can accept a peer's data, only to discard it immediately. A peer will only find out that its data has been discarded when it needs to retrieve backups, at which point it is too late to create new backups.

To combat this, we have designed a challenge system that forces nodes to prove that they are actually storing the data that they are claiming to store. This system is based on the mechanism used in PeerStore \cite{PeerStore}. A challenge in our system consists of a randomly-generated salt followed by a specified range of bytes in the file being backed up. The node holding the peer's data must take the bytes in the specified range, hash it using the provided salt, and return the result to the peer. The peer is able to test whether the answer is correct by encrypting the file in the same way as it is stored on the node and hashing the byte range accordingly. If the correct answer is returned, then the node has passed the challenge. If the node does not respond or gives the wrong answer, the challenge has been failed. By choosing a random subset of bytes and by using a salt, the node cannot calculate the hash ahead of time and only store that; the whole file must be stored in order to be able to successfully complete all possible challenges.
